Part B-2

### 2025-09-08 msca-pf-part-b2-template.tex
feat: move cv example commands to template

>>>>

You may modify the template below as necessary to include all relevant information.

\subsubsection*{Education}
\label{ssc:cv:education}

\begin{cvitem}
\cventry{DD/MM/YYYY DD/MM/YYYY}{Ph.D. in Aerospace Engineering}{University Name}{Location}
\cvdetail{Title}{Title of my Ph.D}
\cvdetail{Advisor}{John Doe}
\end{cvitem}

\subsubsection*{Positions}

\begin{cvitem}
\cventry{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}
\cvdetail{Description}{Job description in short}
\end{cvitem}

% example of a bare entry (same as above without the details)
\cventryitem{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}

\subsubsection*{Publications}

\begin{cvitem}
\cvpub{DD/MM/YYYY}{John Doe, Jane Doe}{Title of the Paper}
                  {Journal Name, Vol. XX, pp. XX--XX}
\cvdetail{Description}{Main findings of the paper}
\cvdetail{URL}{DOI or arXiV URL}
\end{cvitem}

% example for a bare publication (same as above without the details)
\cvpubitem{DD/MM/YYYY}{John Doe, Jane Doe}{Title of the Paper}
                      {Journal Name, Vo. XX, pp. XX--XX}
